Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-05 paper/paper.tex

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.}
If the system is unstable,
i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, then the {\sc verify}
phase will provide values for each coefficients of $\hat{N_{G}(z)}$ and $\hat{D_{G}(z)}$,
which make the closed-loop system unstable.

>>>>

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$,
which make the closed-loop system unstable. This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
